%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,Times New Roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.83]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\recomputelengths
\fancyfoot{}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[RE,LO]{\footnotesize }


\usepackage{import}

% personal data
\name{Bichong}{Li}
\title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{Danling Street No.5, Haidian District, Beijing, China, 100080}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+86 15801062298}                   % optional, remove / comment the line if not wanted
\phone[fixed]{+86 01059172704}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                    % optional, remove / comment the line if not wanted
\email{bichongl@microsoft.com} 
\homepage {aka.ms/bichong}                                % optional, remove / comment the line if not wanted
\social[github]{libichong}
%\photo[84pt]{C:/Users/bichongl/Desktop/me.jpg}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
\extrainfo{Applying for SDE 2}
%\quote{"If you do what you've always done, you'll get what you've always gotten." -- Anthony Robbins}

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\thispagestyle{empty}

\section{Work Experience}

\subsection{Previous Employment}

\vspace{2pt}

\begin{itemize}

\item{\cventry{Jul 2012 -- Now}{Software Development Engineer 2}{Microsoft}{Beijing}{}{\vspace{2pt}I am working in Bing Multimedia Index Generation team. I am responsible for video processing pipeline system and work with 30+ vendors to guarantee their index quality. I have completed the following remarkable projects during the past 3.5 years: 
\vspace{2pt}
\begin{itemize}
\item{Video Page Classifier: analyze html page content to find enough features and use libsvm to train a classifier to distinguish video pages from none video pages. }
\vspace{2pt}
\item{Template Feature Extraction Pipeline v2: transform around 2000 sites from the existing regex matching templates into wrapstar models automatically and integrate them into video crawler, which is the core of feature extraction to guarantee the index quality.}
\vspace{2pt}
\item{BlueWhale Superfresh Video Processing Pipeline: implement the video processing components in Bing baja platform with event processor (similar with windows messagse). Consequently, the index size is doubled and the publish time is decreased from 1 hour to 5 minutes with 90\% coverage.}
\vspace{2pt}
\item{Thumbnail Repository: extract 30 key frames as video thumbnails dumped with ffmpeg library, compute 82 features with image understanding library on each frame, upload the content features and key frames to cosmos platform where they are compressed into SSTREAM(NoSQL). It is the largest repository of video thumbnails and thumbnail content features. The storage platform includes about 20B thumbnails and features and the total physical size is about 4PB.}
\vspace{2pt}
\item{Multimedia Repository v2: implement a storage platform(NoSQL) to store all kinds of features with strong type support to benefit the cosmos SSTREAM serialization and deserialization. The PN hours and storage size are decreased by 29\% and 20\% respectively.}
\vspace{2pt}
\item{Video Feed Processing Pipeline v2: redesign the feed processing pipeline with more flexible components. It doubles the discovery coverage and the traffic goes up by 5 times.}
\vspace{2pt}
\item{Video Expiry Pipeline: detect expired videos with several methods and blocking them in 2 hours which improves the video block latency and DCG metrics significantly.}
\vspace{2pt}
\end{itemize}
In addition, I completed a few terrific tools to facilitate the usage of our video index:
\begin{itemize}
\item{Multimedia Repository Reader: A website to fast deserialize the index content which can help colleagues to analyze instrumental log to debug the pipeline problem.}
\vspace{2pt}
\item{WrapStar Monitor: A set of tools to monitor our templates' quality to help vendors open bugs when the templates are out of order.}
\vspace{2pt}
\item{Auto Onebox: A set of services to help our vendors to verify the correctness of the template check-in.}
\vspace{2pt}
\item{Thumbnail Repository Monitor: A set of graphs to monitor many dimensions of thumbnail repository: each feature's coverage,  physical size and merge time.}
\vspace{2pt}
\item{Auto Checkin Monitor: A tool to monitor the files those are checked in automatically to avoid livesite.}
\vspace{2pt}
\item{Task Scheduler Monitor: A website to manage the running windows tasks.}
\end{itemize}
}}

\vspace{4pt}

\item{\cventry{Dec 2011 -- Jul 2012}{Intern}{Microsoft}{Beijing}{}{\vspace{2pt}I proposed a method to effectively distinguish videos from huge web documents with ~90\% precision and ~80\% recall, which tokenizes the html content into variable words and utilizes tf-idf to catch the importance of a word. I created a set of labelling tools to help our vendors to improve the labelling productivity. It brought an astonishing effect and the manager decided to build a labelling team.}}

\vspace{4pt}

\item{\cventry{Apr 2010 -- Oct 2011}{Software Engineer Intern}{Jiangsu Security Research Institute}{Nanjing, Jiangsu}{}{\vspace{2pt}I was responsible to develop some components of Windows Forensic System, which included
\begin{itemize}
\item{Windows Regedit hive scanner: scan windows regedit in hive level to search sensitive confidential information.}
\vspace{2pt}
\item{Web browser log scanner: scan and analyze the browser history, bookmarks and extensions of IE, firefox and chrome browser. }
\vspace{2pt}
\item{Anti-Virus software log scanner: scan the killing and isolation history by analyzing the log file structure of anti-virus softwares.}
\vspace{2pt}
\item{Windows services scanner: scan windows driver list to expose the hidden windows services. }
\vspace{2pt}
\item{Forensic Communication Services: transfer and import the forensic results to SQL server when standalone clients finish detection process using the technologies including ActiveX control, libXml, ATL framework, Windows IOCP and socket programming.}
\vspace{2pt}
\end{itemize}}}

%\vspace{4pt}
%
%\item{\cventry{Janl 2009 -- Jun 2009}{Software Engineer}{Jiangsu Huazhao Information Co., Ltd}{Nanjing, Jiangsu}{}{\vspace{3pt}My work is to lead a team to implement a bidding client for medicine companies by using .net remoting and .net Entity Framework.}}

\vspace{4pt}

\item{\cventry{Jul 2008 -- Jun 2009}{Software Engineer}{Jiangsu GETO Information Technology Co., Ltd}{Nanjing, Jiangsu}{}{\vspace{2pt}My work was to develop the ERP(Enterprise Resource Planning) and OA(Office Automation) softwares customised for the enterprises using delphi, SQL Server, Oracle, EJB.}}

\end{itemize}

\vspace{2pt}

\subsection{Microsoft Hackathon Projects}

\begin{itemize}

\item{\cventry{2015}{Beijing}{WeWatch}{}{}{\vspace{2pt} WeWatch provides a wide variety of emoticons, gifs and images for you to express feelings in a proactive, intelligent and simultaneous way while watching a video. Every time you start typing comments, emotional pictures will be automatically searched, matched and displayed.}}

\item{\cventry{2014}{Beijing}{BumbleBing, SECOND place in consumer category}{}{}{\vspace{2pt} BumbleBing empowers users to engage in colourful chats with a collection of automatically suggested short video clips based on the context. These short clips are excerpts from top movies and TV shows, encompassing a wide range of emotions and moments.
}}
\item{\cventry{2013}{Beijing}{OneWeb}{}{}{\vspace{2pt} OneWeb is a user-friendly Bing interface that organizes the search results, such as the wiki, high-relevant images and videos, hot discussions and popular comments, into the form of a magazine or a notebook.}}

\item{\cventry{2012}{Beijing}{3DWorldNews}{}{}{\vspace{2pt} 3DWorldNews is a three-dimensional earth pinned by lots of news, especially in the form of image and video. You can rotate, zoom and switch the earth to see fantastic news all around the world.}}

\end{itemize}


\vspace{4pt}

\section{Education}

\vspace{4pt}

\subsection{Academic Qualifications}

\vspace{4pt}

\begin{itemize}

\item{\cventry{2009--2011}{Computer Science and Technology}{Nanjing Normal University}{Nanjing, Jiangsu}{\textit{Master Degree}}{Thesis: \textit{Analysis and Detection of Winodws Nt6.x Rootkits.}}{}}

\item{\cventry{2004--2008}{Electrical and Automation Engineering}{Nanjing Normal University}{Nanjing, Jiangsu}{\textit{Bachelor Degree}}{Thesis: \textit{Data Acquisition System Based on USB Interface.}}{}}

\end{itemize}

\vspace{2pt}

\subsection{Awards and Honours}

\vspace{4pt}

\begin{tabular}{lll}
National Postgraduate Mathematical Modelling Contest $\quad$ & Second Prize $\quad$ & 2011\\
American Mathematical Modelling Contest $\quad$ & Honourable Mentions $\quad$ & 2008\\
Nanjing Normal University Mathematical Modelling Contest $\quad$ & First Prize $\quad$ & 2007\\
Nanjing Normal University Volunteering Teacher $\quad$ & Best Individual Prize $\quad$ & 2005 \\
Nanjing Normal University Debating Competition $\quad$ & Second Prize $\quad$ & 2004
\end{tabular}

\section{Technical and Personal skills}

\vspace{4pt}

\begin{itemize}

\item \textbf{Basic Programming Skills:} Proficient in: Linux BASH Shell, MATLAB, Batch Scripts, Emacs, Python, Powershell, LATEX, Git, SVN, Perl

\vspace{4pt}

\item \textbf{Professional Programming Skills:} Windows Driver FrameWork/BOOST/STL/MFC, C/C++/C\#, SQL/SCOPE, ASP.NET/PHP/JavaScript/CSS/JQuery, WinDBG/Visual Studio/IDA/OllyDBG

\vspace{4pt}

\item \textbf{General Business Skills:} Good presentation skills, Works well in a team.

\end{itemize}

\section{Other Experience}

\vspace{4pt}

\begin{itemize}

\item{To be a Volunteer Teacher in Caohou Village Primary School, Nanjing, Jiangsu. From Sep 2005 to Jun 2006}

\vspace{4pt}

\item{To be an engineer assitant of Prof.Wang Qiong to develop the Adhesive Dispenser II software by using the Visual Basic module based on Motion Control Card MPC02. From Sep 2006 to Dec 2006. }

\end{itemize}




% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------
\thispagestyle{plain}
\end{document}


%% end of file `template.tex'.
